Handbook streamFind: backend

### 2022-10-06 handbooks/Handbook_backend_streamFind.Rmd
LFU17 Updated Classes

@@

The slots analysis, file and replicate correspond to the analysis name, the full file path and the replicate group name, respectively. The metadata slot is a list of objects with informative entries of the analysis file. The metadata list can be expanded with additional information about the analysis/sample (e.g., sample location, weather conditions, process sensor data, etc.). The slot parameters is used to store processing steps (e.g., peak picking) as _settings_ S4 class objects, including the processing step name/ID, the algorithm used and the respective settings applied. The parameters can be used for history track but also for re-run the processing steps when required. The spectra and chromatograms slots are used to store low level data (i.e., mass traces either in profile or centroided modes) from the MS files. Finally, the peaks slot is used to store the chromatographic peaks after peak picking. As no other processing step was applied the spectra, chromatograms and peaks tables in the _msAnalysis_ are empty for now.

@@

An essential aspect of environmental analysis is to operate with sample/analysis replicates. The replicates in _msData_ or _msAnalysis_ can be obtained by the `replicateNames` S4 method as shown below. The setter (assignment) for the replicate names is demonstrated below with the method `replicateNames<-` that takes a vector of character strings with the same length as the number of analyses in a _msData_ object or length one for a single analysis in _msAnalysis_. Alternatively, a table with a replicate character column or a character vector can be given in the files or replicates arguments, respectively.

@@

#setter for replicate names in msData
replicateNames(sp2) <- c(rep("blank", 3),rep("influent", 3))  
replicateNames(sp2)

#setter for replicate name in msAnalysis
a2 <- getAnalyses(sp2, 4)
replicateNames(a2) <- "wastewater"

#getter for replicate name in msAnalysis
replicateNames(a2)
```

@@

The blank subtraction is another crucial aspect in environmental analysis. The getter and setter for blank subtraction works the same way as replicates. See examples below. The blank analysis replicate is then assign to the respective analysis. In the example, the first replicate group is assign to the influent samples. Note that the blank will also be assigned to itself. Although not shown, different blank analysis replicates can be assigned to different analysis. The blank subtraction (\@ref(filter-functions)) is then applied per analysis replicate considering the assigned blank replicate. Getting and assigning blank replicates from an _msAnalysis_ is also possible. However, assigning a blank without the context of a _streamSet_ and without the structure of _msData_ or similar level classes is not recommended. For cross project analysis, a subset of the analyses (_msAnalysis_ objects) in a given _msData_ can be concatenated to another _msData_, carrying the assigned blank replicate for each analysis as well as all the other analysis information (see `r # TODO make section cross project analysis``section cross project analysis for more information).

@@

#setter for the blank analysis replicate of msData object
blankReplicateNames(sp2) <- rep("blank", 6)
blankReplicateNames(sp2)

#getter for msAnalysis
blankReplicateNames(a2)
```

@@

@@

```{r recursive-integration-inspection}
# inspecting the filled peaks for a given mz and rt target
plotFeaturePeaks(sp2_pg_fl, mz = 441.1670, rt = 916, ppm = 20, sec = 60)
```

>>>>

```{r libraries-dev, eval=FALSE, include=FALSE, cache=FALSE}
#for development only
library(data.table)
library(xml2)
library(checkmate)
library(stringr)
library(tools)
library(dplyr)
library(xcms)
library(patRoon)
```

@@

The slot analysis corresponds to the analysis name. The metadata slot is a list of objects with informative entries of the analysis file. The metadata list can be expanded with additional information about the analysis/sample (e.g., sample location, weather conditions, process sensor data, etc.). The slot parameters is used to store processing steps (e.g., peak picking) as _settings_ S4 class objects, including the processing step name/ID, the algorithm used and the respective settings applied. The parameters can be used for history track but also for re-run the processing steps when required. The spectra and chromatograms slots are used to store low level data (i.e., mass traces either in profile or centroided modes) from the MS files. Finally, the peaks slot is used to store the chromatographic peaks after peak picking. As no other processing step was applied the spectra, chromatograms and peaks tables in the _msAnalysis_ are empty for now.

@@

An essential aspect of environmental analysis is to operate with sample/analysis replicates. The replicates in _msData_ can be obtained by the `replicateNames` S4 method as shown below. The setter (assignment) for the replicate names is demonstrated below with the method `replicateNames<-` that takes a vector of character strings with the same length as the number of analyses in a _msData_ object. Alternatively, a table with a replicate character column or a character vector can be given in the files or replicates arguments, respectively. Note that _msAnalysis_ doesn't contain information about replicate correspondence. The correspondence between analyses is storage in the _msFeatures_ within the _msData_.

@@

#setter for replicate names in msData
replicateNames(sp2) <- c(rep("blank", 3),rep("influent", 3))  
replicateNames(sp2)
```

@@

The blank subtraction is another crucial aspect in environmental analysis. The getter and setter for blank subtraction works the same way as replicates. See examples below. The blank analysis replicate is then assign to the respective analysis. In the example, the first replicate group is assign to the influent samples. Note that the blank will also be assigned to itself. Although not shown, different blank analysis replicates can be assigned to different analysis. The blank subtraction (\@ref(filter-functions)) is then applied per analysis replicate considering the assigned blank replicate. For cross project analysis, a subset of the analyses (_msAnalysis_ objects) in a given _msData_ can be concatenated to another _msData_, carrying the assigned blank replicate for each analysis as well as all the other analysis information (see `r # TODO make section cross project analysis``section cross project analysis for more information).

@@

#setter for the blank analysis replicate of msData object
blankReplicateNames(sp2) <- rep("blank", 6)
blankReplicateNames(sp2)
```

@@

`r # TODO list all S4 methods``

@@

`r # TODO find another example for filling results`

```{r recursive-integration-inspection}
# inspecting the filled peaks for a given mz and rt target
plotFeaturePeaks(sp2_pg_fl, mz = 441.1670, rt = 1097, ppm = 20, sec = 60)
```
